\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-03 doc/flexiblesusy-paper.tex
swap sections 8.1 (speed test) and 8.2 (numeric tests)
explain difference to Softsusy (w/o flavour violation)
The differences are:

 * calculation of the weak mixing angle (FS uses MW and MZ, while
   Softsusy uses the muon decay)

 * some two-loop threshold corrections in Softsusy, missing in FS

 * some three-loop beta-functions in Softsusy

@@

To check the correctness of \fs's generated spectrum generators
extensive unit testing against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
was carried out. We checked mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles and found all to agree within double machine
precision.  We also compared the overall pole mass spectrum after the
full fixed-point iteration has finished, and found the spectra to
agree at the sub-permille level.

\fs generated NUHM \ESSM has also been compared against a handwritten
spectrum generator for a constrained version of the \ESSM
\cite{Athron:2009ue, Athron:2009bs, Athron:2012pw}.  The RGEs could be
compared directly in unit tests and were found to match.  The
handwritten code doesn't include full one-loop self-energies or
tadpoles so tests on these were not carried out.  Although the
generators assume different constraints they could be compared by
using the output of the CE$_6$SSM generator as an input to \fs and the
spectra were found to be in reasonable agreement, given the different
levels of precision.

>>>>

To check the correctness of \fs's generated spectrum generators
extensive unit testing against Softsusy's MSSM and NMSSM
implementations (both $Z_3$-invariant and $Z_3$-violating variants)
was carried out.  These unit tests systematically compare all
tree-level mass matrices, EWSB equations, one- and two-loop
$\beta$-functions, one- and two-loop self-energies and one- and
two-loop tadpoles numerically for certain MSSM and NMSSM parameter
points.  All tested expressions were found to agree within double
machine precision.\footnote{Due to the systematic and detailed tests
  several bugs in Softsusy, SARAH and \fs could be identified and
  corrected.}  Furthermore, the overall pole mass spectrum after the
full fixed-point iteration has finished is compared, and was found to
agree at the sub-permille level.  The origin of the sub-permille level
difference between \fs and Softsusy is the different determination of
the \DRbar\ weak mixing angle
$\theta_{W,\text{susy}}^{\text{\DRbar}}(M_Z)$: \fs calculates
$\theta_W$ from $M_W^2$ and $M_Z^2$ as described in
\secref{sec:calculation-of-gauge-couplings}, while Softsusy determines
$\theta_W$ from the muon decay constant $G_\mu$, which is more
precise.  Furthermore, in Softsusy $3.5.0$ some three-loop
$\beta$-functions and two-loop threshold corrections for the gauge and
Yukawa couplings can be enabled in the MSSM to increase the accuracy
of the RG running and the \DRbar\ gauge and Yukawa couplings at $M_Z$
\cite{}.  These corrections are not implemented in \fs so far.

The complete set of unit tests is shipped with \fs and can be found in
the \code{test/} directory.  The tests can be run with the command
\code{make execute-tests}.  All unit tests are carried out nightly in
order to continuously check the correctness of the meta code and the
generated spectrum generators.  The test results can be found at
\url{http://iktp.tu-dresden.de/~avoigt/FlexibleSUSY/FlexibleSUSY/test.html}

The \fs generated NUHM \ESSM\ spectrum generator has also been
compared against a handwritten one for a constrained version of the
\ESSM \cite{Athron:2009ue, Athron:2009bs, Athron:2012pw}.  The
$\beta$-functions were systematically compared in unit tests and were
found to match at the ??? level.  The handwritten code doesn't include
full one-loop self-energies or tadpoles, so tests on these were not
carried out.  Although the generators assume different constraints
they could be compared by using the output of the CE$_6$SSM generator
as an input to \fs and the spectra were found to be in reasonable
agreement, given the different levels of precision.

@@
